\documentclass[10pt,a4paper]{article}

% ==========================================
% PACKAGES
% ==========================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage[margin=1cm]{geometry} % Thin margins to fit on one page
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

% ==========================================
% COLORS & DESIGN
% ==========================================
% Main CV Color (EPITA Blue / Tech)
\definecolor{primary}{RGB}{0, 80, 213} 
\definecolor{darkgray}{RGB}{51, 51, 51}

\hypersetup{
    colorlinks=true,
    linkcolor=primary,
    filecolor=primary,
    urlcolor=primary,
}

% Section title format
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}

% Ultra-compact list spacing
\setlist[itemize]{leftmargin=1.5em, itemsep=0pt, topsep=1pt, parsep=0pt, partopsep=0pt}

\begin{document}
\pagestyle{empty} % Remove page numbers

% ==========================================
% HEADER
% ==========================================
\begin{center}
    {\huge \textbf{Noah CIVILISE}}\\[2pt]
    {\large \textbf{5\textsuperscript{th}-year Student at EPITA -- Computer Science Engineering}}\\[4pt]
    
    {\footnotesize
    \ \textbullet\
    \href{mailto:civilise.noah@gmail.com}{civilise.noah@gmail.com} \ \textbullet\ 
    +33 6 60 39 97 86 \ \textbullet\ 
    \href{https://www.linkedin.com/in/noah-civilise/}{LinkedIn} \ \textbullet\ 
    \href{https://github.com/Noah30c}{GitHub} \ \textbullet\ 
    \href{https://civilise-noah.onrender.com/}{Portfolio}
    }
\end{center}

\vspace{0.2cm}

% ==========================================
% OBJECTIVE
% ==========================================
\noindent
\textbf{Objective:} Seeking a 6-month end-of-studies internship in Artificial Intelligence or Image Processing starting from February 2027 in Bordeaux or Paris. Curious, adaptable, and motivated, I wish to deepen my skills in these fields within a stimulating environment.

% ==========================================
% PROFESSIONAL EXPERIENCE
% ==========================================
\section*{Professional Experience}

\noindent
\textbf{Final Year Project (PFEE) -- Virtual Reality Engineer} \hfill \textit{Feb 2026 - Present} \\
\textit{Dassault Systèmes} \\
\textit{Design of a VR navigation tool (Minimap) for complex 3D environments (WebXR).}
\begin{itemize}
    \item Development of an immersive WebXR experience (Three.js, TypeScript) featuring a dynamic VR Minimap.
    \item Implementation of 3D algorithms ("World Detection") and asynchronous optimization via WebWorkers.
\end{itemize}

\vspace{0.1cm}
\noindent
\textbf{Data Science \& Generative AI Intern} \hfill \textit{Sept 2025 -- Jan 2026} \\
\textit{Compagnie Européenne de Garanties et Cautions (Groupe BPCE)}
\begin{itemize}
    \item \textbf{RAG Architecture \& LLMs}: "From scratch" design of an information extraction pipeline for hundreds of PDF balance sheets (SentenceTransformer, Qdrant, LLM).
    \item \textbf{Reliability \& MLOps}: Strict validation of generated data (JSON, Pydantic, Luhn) and tracking of confidence metrics (77.1\%) on a Streamlit dashboard.
    \item \textbf{Automation \& NLP}: Development of an invoice control tool cross-referencing Excel data with text extracted from PDFs analyzed by an LLM (Time saved: >60\%).
    \item \textbf{Industrialization}: Autonomous deployment of the automation tool (PyInstaller) to bypass IT constraints, and data workflow orchestration on Dataiku.
    \item \textbf{Business Intelligence}: Star schema data modeling and creation of a Power BI dashboard (DAX) to automatically detect drifts in bond granting rules.
\end{itemize}

\vspace{0.1cm}
\noindent
\textbf{Tutor} \hfill \textit{2022 -- 2023} \\
\textit{BackToBasics, EPITA}
\begin{itemize}
    \item Tutoring in algorithms, programming, and mathematics (individual and group sessions).
\end{itemize}

% ==========================================
% TECHNICAL PROJECTS
% ==========================================
\section*{Technical Projects}

\noindent
\textbf{Automatic License Plate Recognition (ALPR)} \hfill \textit{C++, Python, OpenCV, ML} \\
"From scratch" development of an ALPR pipeline without Deep Learning. Prototyping (Python) and low-level porting (C++) for optimization (MyCV library, Random Forest, CI/CD). Processing < 380ms with 93\% accuracy.

\vspace{0.1cm}
\noindent
\textbf{DermScan (Medical AI)} \hfill \textit{Python, OpenCV, FastAPI, RabbitMQ, Docker} \\
Distributed dermatological diagnosis aid application (ABCDE rule). Computer vision pipeline (K-Means, PCA) and Machine Learning (MLP, sensitivity >85\%) focused on explainability. Asynchronous microservices architecture with full CI/CD.

\vspace{0.1cm}
\noindent
\textbf{GStreamer Filter (GPGPU CUDA)} \hfill \textit{C++, CUDA, GStreamer} \\
GPGPU optimization of a motion detection video filter. Real-time processing pipeline with CUDA acceleration (CUDA Graphs, Pinned memory).

\vspace{0.1cm}
\noindent
\textbf{Tiger Compiler} \hfill \textit{C++, Flex/Bison, LLVM} \\
Team development of a complete compiler for the object-oriented Tiger language. Modular architecture: lexical/syntactic analysis, semantic verification, and code generation (LLVM IR). Implementation of code optimizations (inlining, escape analysis).

% ==========================================
% EDUCATION
% ==========================================
\section*{Education}

\noindent
\textbf{EPITA – Computer Science Engineering School} \hfill \textit{2022 -- 2027} \\
5\textsuperscript{th} year in Computer Science Engineering - \textbf{GPA: 4.0} \hfill \textit{Le Kremlin-Bicêtre, France}

\vspace{0.1cm}
\noindent
\textbf{Universidad del País Vasco} \hfill \textit{2024} \\
Academic Exchange \hfill \textit{San Sebastián, Spain}

\vspace{0.1cm}
\noindent
\textbf{High School Diploma (Baccalaureate)} \hfill \textit{2019 -- 2022} \\
Mathematics and Computer Science (NSI) -- \textbf{High Honors} \hfill \textit{Montigny-Le-Bretonneux, France}

% ==========================================
% SKILLS
% ==========================================
\section*{Skills}

\begin{itemize}
    \item \textbf{Languages:} C++, Python, TypeScript, Java, C, Bash, HTML/CSS
    \item \textbf{Tools \& Frameworks:} OpenCV, React, FastAPI, Docker, RabbitMQ, CMake, Git, CI/CD
    \item \textbf{Languages:} English (TOEIC 900/990 - Fluent), Spanish (B1), French (Native)
    \item \textbf{Soft Skills:} Adaptability, Teamwork, Autonomy, Problem Solving
    \item \textbf{Miscellaneous:} A2 \& B Driving Licenses
\end{itemize}

\end{document}
